Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-04 lloveras_2020.tex
algo de texto

@@

@@

@@

\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI.
OBS: Esto es valido para hasta la fig 7 inclusive.}

@@

DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, \textcolor{red}{definir hollow-tom} and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.

\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
OBS: Esta es la seleccion para las figuras 8 en adelante. Citar numerical recipes seccion 15.2}

For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them. To that end three different types of magnetic lines corresponding with three different types of magnetic structures where selected:

  0 - Small-closed field lines footlat $<30$ y gradt neg. where most of the DOWN loops showed up before

  I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. gradt pos
   %This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

  II - Large-closed field lines. Large meaning their apex surpasses the DEMT range of heights. This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt. footlat $>30$ y gradt pos

 III - Open field lines. footlat $>60$ y gradt pos

\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}

@@

@@

>>>>

*Paso 1: obtencion de FBE
*Paso 2: obtencion LDEM
\begin{equation}\label{fbeldem}
\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
\end{equation}

@@

*Una medida del grado de acuerdo de la reconstruccion
\begin{equation}\label{R}
R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn} / \,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
\end{equation}

@@

\textcolor{red}{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.}

@@

@@

\textcolor{red}{*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
OBS: SE usan los errores en temp y densidad. Citar numerical recipes seccion 15.2}

\textcolor{red}{Se eligen loops con abs(person temp) mayor a .5 lo cual nos permite descartar loops QI. gradT suficientemente grandes.}

For the two targeted rotations, DEMT and AWSoM resuls were traced along the AWSoM field lines, which provides a way to characterize the global thermodynamic state of the inner solar corona and to compare them. To that end four different types of legs corresponding with four different types of magnetic structures where selected:

  0 - Small (meaning with apex within the DEMT range of heights) closed field lines in the latitudes range $[-30\mdeg,+30\mdeg]$ and $\nabla_r T_m < 0$. This class thoroughly populates the equator of the Streamer belt during a minimum solar rotation.

  I - Small closed field lines in all latitudes, with $\nabla_r T_m > 0$. This class thoroughly populates the inner of the Streamer belt.

  II - Large (meaning their apex surpasses the DEMT range of heights) closed field lines in the latitudes range $[-90\mdeg,-30\mdeg] \cup [+30\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$. This class is mostly populated by very large trans-equatorial field lines forming the envelope of the Streamer belt.

 III - Open (meaning with apex out the DEMT range of heights) field lines in the latitudes range $[-90\mdeg,-60\mdeg] \cup [+60\mdeg,+90\mdeg]$ and $\nabla_r T_m > 0$.

\textcolor{red}{Hice las definiciones con gradiente de temperatura para que quede mas claro, pero en realidad uso el pearson.} 
%\textcolor{red}{que quede claro que de ahora en mas solo consideramos ajustes de loops up, es decir pearson temp > 0.5 debido a que awsom solo tiene up.}

@@

While CR-2082 was highly axisymmetric and showed virtually no ARs\textcolor{red}{(ver si en lat 50 y long 70 hay una.)}, CR-2208 showed an AR around latitude $+10\mdeg$ and longitude $300\mdeg$ \textcolor{red}{(ver la region open en lat 0 y long 200)}. Except for this AR, in both rotations the open-closed boundaries derived from the respective AWSoM model match the shape of the contour levels of the tomographic maps of both the electron density and the electron mean temperature. In these regions, there is a lack of match between the open-closed boundaries and the tomographic reconstructions of density and temperature. This range of longitudes was excluded from the analysis. Closed regions are characterized by relatively larger values of density and temperature in comparison to the open regions.

@@

\textcolor{blue}{seccion 3.5 del otro paper}
